Two sample $t$ test example using `nycflights13` `flights` data

### 2018-06-13 inst/doc/chisq_test.Rmd
Update pkgdown and vignettes

Using `chisq_test` in `infer`

```{r}
obs_chisq <- fli_small %>% 
  chisq_test(formula = origin ~ season) %>% 
  dplyr::select(statistic) %>% 
  dplyr::pull()
```

@@

@@

@@

```{r}
chisq_null_distn %>% 
  dplyr::summarize(p_value = mean(stat >= pull(obs_chisq))) %>% 
  dplyr::pull()
```

>>>>

The recommended approach is to use `specify() %>% calculate()`:

```{r}
obs_chisq <- fli_small %>%
  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
  calculate(stat = "Chisq")
```

@@

Or using `chisq_test` in `infer`

```{r}
obs_chisq <- fli_small %>% 
  chisq_test(formula = origin ~ season) %>% 
  dplyr::select(statistic)
```

Again, the observed $\chi^2$ statistic is `r obs_chisq`.

@@

Lastly, the observed $\chi^2$ statistic is `r obs_chisq`.

@@

```{r}
chisq_null_distn %>% 
  p_value(obs_stat = obs_chisq, direction = "greater")
```

### 2018-06-13 inst/doc/two_sample_t.Rmd
Update pkgdown and vignettes

Using `t_test` in `infer`

@@

```{r}
t_null_distn %>% 
  dplyr::summarize(p_value = mean(abs(stat) >= pull(obs_t))) %>% 
  dplyr::pull()
```

>>>>

The recommended approach is to use `specify() %>% calculate()`:

```{r}
obs_t <- fli_small %>%
  specify(arr_delay ~ half_year) %>%
  calculate(stat = "t", order = c("h1", "h2"))
```

The observed $\chi^2$ statistic is `r obs_chisq`.

Or using `t_test` in `infer`

@@

```{r}
t_null_distn %>% 
  p_value(obs_stat = obs_t, direction = "greater")
```
